# AN588-Homework1-itsjon

# My Attempt into the first homework

# Challenge 1

```{r}
library(stringr) 
ulysses_lines <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
ulysses_remove <- gsub("[[:punct:]]", "", ulysses_lines)
ulysses_words <- str_split(ulysses_remove, " ")[[1]]
every_third_word <- ulysses_words[seq(1, length(ulysses_words), by = 3)]
every_third_word
```

```{r}
# Gentry's comment: "I recommend writing your code in code blocks so you can easily re-run and edit it as your work. You can either use the Insert drop down menu at the top of your editor pane or use the shortcut "ctrl + alt + i" (cmnd + alt + i on mac)"

# My comment: "I did not know I could do that, and I will say, it's so much better this way."
```

# Challenge 2

```{r}
# Suppose m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)

# Extract and assign columns to **x**
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
x <- m[, c(2,3,6)]
x 

# **Rows 6-8:**
x <- m[6:8,]
x 

# **Row 2, Column 2 -\> Row 6, Column 9:**

x <- m[2:6, 2:9] 
x

# Gentry's comment: "Very clean, I didn't know you could index with a list like this. Going back to my first note, another benefit of using code blocks is that you don't need to copy the output because it can easily be reproduced." 

# My Comment: The code blocks really helps it. 
```

# Challenge 3

```{r}
a <- array(400:1, dim = c(5, 5, 4, 4))
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]

# Gentry's comment: "Looking beyond the output, can you describe how do these commands interact with the matrix to produce the results?"

# My comment: "Once I have build my array and put it into a variable, I used it to identify the number list by which row and column they're in, to "pull it out" as a result.  
```

# Challenge 4

```{r}
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Tarsioidea = c("Tarsiidae")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Catarrhini")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
Primates
```

# Challenge 5

```{r}
# **Data Frame**
numbers <- c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2)
m <- matrix(numbers, nrow = 5, ncol = 3, byrow = TRUE)
m

numbers <- c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2)
df <- as.data.frame(m)
df[, 2] <- as.logical(df[, 2])
df[, 3] <- as.factor(df[, 3])
df

str(df)

```

# Comments from me:

1.  Overall, not bad what so ever.
2.  Some technical difficulties at the beginning, but we got through them, albeit, it ended up being a little late. Thanks to my peer for their comments.
3.  Thanks to gentry to telling me about code blocks. Came in handy there.
